\input{hw4.tex}
\begin{document}
\maketitle
\thispagestyle{firststyle}
\vspace{-2.0cm}
\section{More undecidable problems. }
\begin{quote}
    Show that it is undecidable, given the source code of a program $Q$, to tell whether or not any of the following is true:
    \begin{enumerate}[(i)]
      \item $Q$ halts on input 0.
      \item $Q$ is total -- that is, $Q(y)$ halts for all $y$.
      \item $Q(y)=$ {\tt true} for all $y$.
      \item The set of $y$ on which $Q$ halts is finite.
      \item There is a $y$ such that $Q(y)= y$.
      \item Given a second program $R$, $Q$ is equivalent to $R$.
      That is, even though $Q$ and $R$ have different source codes,
      they compute the same partial function --
      for all $y$, either $Q(y)$ and $R(y)$ both halt and return the same answer, or neither halts.
    \end{enumerate}
    Prove each of these by reducing $\textsc{Halting}$ to them.
    That is, show to how convert an instance $(P, x)$ of $\textsc{Halting}$ to an instance of the problem above.
    For instance, you can modify $P$'s source code,
    or write a new program that calls $P$ as a subroutine.
    Each of these is asking for a Turing reduction;
    your reduction does not necessarily have to map yes-instances to yes-instances and no-instances to no-instances --
    all that matters is that if you could solve the problem,
    then you could solve $\textsc{Halting}$.
\end{quote}

\section*{Solution}

\begin{enumerate}[(i)]
    \item We show that HALTING$\leq$ (i)\\
    For the given arbitrary instance $(P, x)$, we build $Q_{P,x}$ like below:
    \begin{lstlisting}[language=python]
    def Q_Px(y):
        if y==0:
           P(x)
        else:
           return
    \end{lstlisting}
    We can see that for any input 0, the program $Q$ will run the problem $P(x)$, the instance of the Halting problem.\\
    So we can get that: $P(x)$ halts $\Leftrightarrow$ $Q_{P,x}(y)$ halts on input 0.
    \item We show that HALTING$\leq$ (ii)\\
    For the given arbitrary instance $(P, x)$, we build $Q_{P,x}$ like below:
    \begin{lstlisting}[language=python]
    def Q_Px(y):
        P(x)
        
    \end{lstlisting}
    We can see that for any input $y$, the program $Q$ will run the problem $P(x)$, the instance of the Halting problem.\\
    So we can get that: $P(x)$ halts $\Leftrightarrow$ $Q_{P,x}(y)$ halts for all $y$.
    \item We show that HALTING$\leq$ (iii)\\
    For the given arbitrary instance $(P, x)$, we build $Q_{P,x}$ like below:
    \begin{lstlisting}[language=python]
    def Q_Px(y):
        if P(x):
           return True
        return False
    \end{lstlisting}
    We can see that $Q(y)=$ {\tt true} for all $y$ if and only if happens when the instance $P(x)$ halts.\\
    So we can get that: $P(x)$ halts $\Leftrightarrow$ $Q_{P,x}(y)=true$ for all $y$.
    \item We show that HALTING$\leq$ (iv)\\
    Unlike the above three proof, this time we need to modify $P(x)$:
    \begin{lstlisting}[language=python]
    def P(x):
        ... (remain unchanged)
        for every i as second/step/configuration:
            Q_Px(i); 
        ... (remain unchanged)
    def Q_Px(i):
        return
    \end{lstlisting}
    So we can see that if $P(x)$ halts, its runninfg time/steps are finite, which makes the input subset of $Q_{P,x}$ finite. Otherwise, if if $P(x)$ never halts, there will be infinite inputs of $Q_{P,x}$.\\
    So we can get $P(x)$ halts $\Leftrightarrow$ The set of $y$ on which $Q_{P,x}(y)$ halts is finite.
    \item We show that HALTING$\leq$ (v)\\
    For the given arbitrary instance $(P, x)$, we build $Q_{P,x}$ like below:
    \begin{lstlisting}[language=python]
    def Q_Px(y):
        if P(x):
           return y
    \end{lstlisting}
    So it is obvious that $P(x)$ halts $\Leftrightarrow$ $Q_{P,x}(y)=y$ exists.
    \item We create a function which checks if two program are equivalent or not:
    \begin{lstlisting}[language=python]
    def check(P,Q):
        if Halts(P(x)) and Halts(Q(x)):
            if P(x)==Q(x):
                return True
            else:
                return False
        if Halts(P(x)) and !Halts(Q(x)):
            return False
        if !Halts(P(x)) and Halts(Q(x)):
            return False
        if !Halts(P(x)) and !Halts(Q(x)):
            return True
    \end{lstlisting}
    It is obvious that $check(P,Q)$ is decidable $\Leftrightarrow$ Halting(Halts()) is decidable. So that if we could solve this check equivalence problem, then we could solve $\textsc{Halting}$.
\end{enumerate}

\end{document}