\subsection*{Existence, search, and the oracle. (Textbook problem 1.10)}
    \begin{quote}
    We can consider two rather different problems regarding Hamiltonian cycles (note a Hamiltonian \emph{cycle} must start and end at the same vertex). One is the decision problem, the yes-or-no question of whether such a cycle exists. The other is the search problem or function problem, in which we want to actually find the cycle. However, the hardness of these problems is very closely related.

    Suppose that there is an oracle in a nearby cave. She will tell us, for the price of one drachma per question, whether a graph has a Hamiltonian cycle. If it does, show that by asking her a series of questions, perhaps involving modified versions of the original graph, we can find the Hamiltonian cycle after spending a number of drachmas that grows polynomially as a function of the number of vertices. Thus if we can solve the decision problem in polynomial time, we can solve the search problem as well.
    \end{quote}

\solution

The intuition of the solution is that a Hamiltonian cycle is deterministic, which will not be affected by other edges existance.
In other words, if an edge is not in a Hamiltonian cycle, remove it will not affect the result.
However, if a graph have multiple Hamiltonian cycles(think of a 4-click), we are free to destroy one cycle and the other will survive. 
We shall present the proof later.

Now we can conduct the following algorithm:

\begin{algorithm}
\caption{Get Hamiltonian Cycle with the help of an Oracle}
\begin{algorithmic}
	\REQUIRE $G = (E, V)$
	\STATE $H \leftarrow E$
	\FOR {$\forall e \in E$} 
		\IF {Oracle($G(H / \{e\}, V)$) == true} 
			\STATE $H \leftarrow H / \{e\}$
		\ENDIF
	\ENDFOR
	\RETURN $H$
\end{algorithmic}
\end{algorithm}

Now let's proof that this algorithm is correct:

\begin{proof}
Suppose a true Hamiltonian cycle is $H'$.

First, it is trivial to see that during removing process, remove a non-Hamiltonian edge will not nullify previous preserved Hamiltonian edge.

Therefore we can see that $G' = (H, V)$ have a Hamiltonian cycle, or else $H = \emptyset$ and $G$ has no Hamiltonian cycle(i.e. $H' = \emptyset$ too), leading to $H' \subset H$.

Now we want to prove that $H \subset H'$.

Suppose we have $h \in H, h \notin H'$. But this is impossible as it should have been removed in the algorithm, since \texttt{Oracle($G(H / \{h\}, V)$) == true}.

So we have $H == H'$, the subset of edges we picked should be Hamiltonian cycle.

\end{proof}

Now if the Oracle can solve this in $\P$, since we only do $O(|E|) = O(|V|^2)$ queries to, the overall time complexity is still in $\P$. 